---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `gargap` (`gar`goyle `a`pp-`p`ackage)

<!-- badges: start -->

<!-- badges: end -->

The goal of `gargap` is to demonstrate the [`gargoyle` package](https://github.com/ColinFay/gargoyle) using modules (within in a package). Hence the name: **gar**goyle **a**pp-**p**ackage.

## Modules

The modules are stored in `mod_button` and `mod_table`:

```{r echo=FALSE}
fs::dir_tree("R", regexp = "mod")
```

## UI & Server

The application UI and server are stored in separate functions:

```{r echo=FALSE}
fs::dir_tree("R", regexp = "gargo")
```

## Standalone app function

To run the application, use the `launchApp()` function:

```{r echo=FALSE}
fs::dir_tree("R", regexp = "App")
```

```{r example, eval=FALSE}
library(gargap)
gargap::launchApp()
```

# Installation

You can install the development version of `gargap` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mjfrigaard/gargap")
```

## Deployed Example

View a deployed version of the application [here](https://mjfrigaard.shinyapps.io/gargap/):
